---
title: "Lab 01 - Hello R"
author: "zheqi"
date: "1/13/2023"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

A data frame with 1846 rows and 3 variables.

### Exercise 2

dino_data <- datasaurus_dozen %>%
+     filter(dataset == "dino")
> ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
+     geom_point()
> dino_data %>%
+     summarize(r = cor(x, y))
# A tibble: 1 × 1
        r
    <dbl>
1 -0.0645
> #> # A tibble: 1 × 1
> #>         r
> #>     <dbl>
> #> 1 -0.0645
First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

 star_data <- datasaurus_dozen %>%
+     filter(dataset == "star")
> ggplot(data=star_data, mapping = aes(x = x, y = y))+
+     geom_point()
> star_data %>%
+     summarize(r = cor(x, y))
# A tibble: 1 × 1
        r
    <dbl>
1 -0.0630
```{r plot-star, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
   filter(dataset == "star")
ggplot(data=star_data, mapping = aes(x = x, y = y))+
   geom_point()

star_data %>%
  summarize(r = cor(x, y))
```
### Exercise 4

circle_data <- datasaurus_dozen %>%
+     filter(dataset == "circle")
> ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
+     geom_point()
> circle_data %>%
+     summarize(r = cor(x,y))
# A tibble: 1 × 1
        r
    <dbl>
1 -0.0683
```{r plot-circle, fig.height=3, fig.width=6}
circle_data <- datasaurus_dozen %>%
   filter(dataset == "circle")
ggplot(data=circle_data, mapping = aes(x = x, y = y))+
   geom_point()
circle_data %>%
  summarize(r = cor(x, y))
```


### Exercise 5

```{r plot-all, fig.height=6, fig.width=3}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
   geom_point()+
   facet_wrap(~ dataset, ncol = 3) +
   theme(legend.position = "none")
datasaurus_dozen %>%
   group_by(dataset) %>%
   summarize(r = cor(x, y)) %>%
   print(13)
knitr::opts_chunk$set(echo = TRUE)
```



## Bonus Tips by Yoo Ri

Here are some helpful tips :) 

* filter() is for extracting rows

* group_by() is for grouping datasets by assigned column 
* ungroup() cancels the grouping 

* summarize()  is often used with group_by(). This function can print the output according to the group_by().

* facet_grid(y~x,...) creates a grid with variable y as a row, variable x as a column  
* facet_wrap(x,... ) is useful when there is only one variable